Blocking-resistant communication\\through domain fronting

### 2014-11-23 docs/meek.tex
Make it clear the Psiphon deployment was independent.
Remember to ack Sadia and Michael.
Apply ACM style and make necessary formatting tweaks.
Use the alternate ACM style.
Tighten up.

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting}
\caption{
Domain fronting uses different domain names at different layers of communication.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor but meaningful to the intermediate web service,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

@@

\section{Architecture and protocol of \meek}
\label{sec:architecture}

@@

\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9\x9f...
\end{verbatim}
\smallskip
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 739

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75\xa2...
\end{verbatim}
\end{quote}
\smallskip
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 0

\end{verbatim}
\smallskip
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 75

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on their handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
shows two browsers which have TLS fingerprints different from Go's
and different from each other's.
A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

\begin{figure*}
\centering
\begin{subfigure}[t]{0.30\textwidth}
\caption{Go 1.2's crypto/tls library}
\begin{minipage}[t][25.5ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
Extensions:
  server_name
  status_request
  elliptic_curves
  ec_point_formats
  signature_algorithms
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:golang}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\caption{Firefox 24}
\begin{minipage}[t][57ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_DHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_DSS_WITH_AES_128_CBC_SHA
  TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
  TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
  TLS_DHE_RSA_WITH_AES_256_CBC_SHA
  TLS_DHE_DSS_WITH_AES_256_CBC_SHA
  TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
  TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
  TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_ECDSA_WITH_RC4_128_SHA
  TLS_ECDH_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
  TLS_RSA_WITH_SEED_CBC_SHA
  SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_RC4_128_MD5
Extensions:
  server_name
  renegotiation_info
  elliptic_curves
  ec_point_formats
  SessionTicket TLS
  next_protocol_negotiation
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\caption{Chrome 33}
\begin{minipage}[t][42.5ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
  TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
  TLS_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_DHE_RSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_DSS_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_RC4_128_MD5
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
Extensions:
  server_name
  renegotiation_info
  elliptic_curves
  ec_point_formats
  SessionTicket TLS
  next_protocol_negotiation
  application_layer_protocol_negotiation
  Channel ID
  status_request
  signature_algorithms
  Signed Certificate Timestamp
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:chrome}
\end{subfigure}

@@

\section{A survey of fronting-capable web services}
\label{sec:survey}

@@

$$\diamondsuit$$

@@

[Blinded circumvention tool]
% ANON
% Psiphon
began their deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek%
,
% ANON
% with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-%
[blinded circumvention tool],
% ANON
% Psiphon,
with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release.

@@

% We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
% Special thanks go to the members of the tor-qa and tor-dev mailing lists
% who responded to our design ideas, reviewed source code, and tested our prototypes.
% Thanks to Psiphon~Inc. for help with design and development, and for providing user count estimates.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Ox from Lantern.
% Johanna Amann for getting the fraction of SNI from ICSI notary:
%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
% Arlo Breault (flashproxy-reg-appspot)

@@

\bibliographystyle{IEEEtran}
\bibliography{meek}

>>>>

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}

% Turn off ACM copyright block.
\toappear{}

\urlstyle{same}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting}
\caption{
Domain fronting uses different domain names at different layers.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

@@

\section{Architecture and protocol of meek}
\label{sec:architecture}

@@

\x16\x03\x01\x02\x00\x01\x00\x01\xfc\x03\x03\x9b\xa9...
\end{verbatim}
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 739

\x16\x03\x03\x00\x3e\x02\x00\x00\x3a\x03\x03\x53\x75...
\end{verbatim}
\end{quote}
\begin{verbatim}
POST / HTTP/1.1
Host: forbidden.example
X-Session-Id: cbIzfhx1Hn+RHURmIPhjgY+W3B6zA8Ua6dd92DLscOE=
Content-Length: 0

\end{verbatim}
\begin{quote}
\begin{verbatim}
HTTP/1.1 200 OK
Content-Length: 75

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on their handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} in Appendix~\ref{sec:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome}
show two browsers which have TLS fingerprints different from Go's
and different from each other's.
A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

\section{A survey of fronting-capable\\web services}
\label{sec:survey}

@@

% $$\diamondsuit$$

@@

[Blinded circumvention tool]
% ANON
% Psiphon
began their independent deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek%
,
% ANON
% with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-%
[blinded circumvention tool],
% ANON
% Psiphon,
with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release.

@@

% We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
% Special thanks go to the members of the tor-qa and tor-dev mailing lists
% who responded to our design ideas, reviewed source code, and tested our prototypes.
% Thanks to Psiphon~Inc. for help with design and development, and for providing user count estimates.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Ox from Lantern.
% Johanna Amann for getting the fraction of SNI from ICSI notary:
%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
% Arlo Breault (flashproxy-reg-appspot)
% Sadia Afroz and Michael Tschantz

@@

\bibliographystyle{abbrv}
\bibliography{meek}

\appendix

\section{Sample TLS fingerprints}
\label{sec:ciphersuites}

Figure~\ref{fig:ciphersuites} illustrates the need for camouflage at the TLS layer.
Even though the TLS application data is effectively hidden by encryption,
the plaintext parts of TLS reveal information about the implementation.
The TLS must not be easily identified as belonging to a circumvention tool.

\begin{figure*}
\centering
\begin{subfigure}[t]{0.30\textwidth}
\caption{Go 1.2's crypto/tls library}
\begin{minipage}[t][25.5ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
Extensions:
  server_name
  status_request
  elliptic_curves
  ec_point_formats
  signature_algorithms
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:golang}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\caption{Firefox 24}
\begin{minipage}[t][65ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_DHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_DSS_WITH_AES_128_CBC_SHA
  TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
  TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
  TLS_DHE_RSA_WITH_AES_256_CBC_SHA
  TLS_DHE_DSS_WITH_AES_256_CBC_SHA
  TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
  TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
  TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_ECDSA_WITH_RC4_128_SHA
  TLS_ECDH_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
  TLS_RSA_WITH_SEED_CBC_SHA
  SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_RC4_128_MD5
Extensions:
  server_name
  renegotiation_info
  elliptic_curves
  ec_point_formats
  SessionTicket TLS
  next_protocol_negotiation
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\caption{Chrome 33}
\begin{minipage}[t][42.5ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
  TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
  TLS_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_DHE_RSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_DSS_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_RC4_128_MD5
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
Extensions:
  server_name
  renegotiation_info
  elliptic_curves
  ec_point_formats
  SessionTicket TLS
  next_protocol_negotiation
  application_layer_protocol_negotiation
  Channel ID
  status_request
  signature_algorithms
  Signed Certificate Timestamp
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:chrome}
\end{subfigure}
